$Z_3$ topological order in the quantum dimer-pentamer model

### 2016-05-08 qdpm_paper.tex
New figure of magnetic strings.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tpb]
    \centering
    \includegraphics[width=0.5\columnwidth]{QDPM_ex_config.pdf}
    \caption{\textcolor{red}{Replace with a figure showing the orientations of the lattice links, with an open oriented string on the dual lattice as well as a closed oriented loop and topologically non-trivial loops.}The link orientations of the square lattice.}
    \label{fig:orientedSL}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c | c |}
  	\hline
    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
	\hline
    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
	\hline
    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
	\hline
    trimer & $2$ & 1 & 0 &  $\svrttrmr $ \\
	\hline
    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
	\hline
    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\newcommand*{\svrttrmrtwo}{%
    ]{Symbols/sing_vrt_trimer2.pdf} }

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tpb]
    \centering
    \includegraphics[width=1.0\columnwidth]{mag_loops_on_orntd_lat.pdf}
    \caption{Three oriented magnetic strings on the square lattice. From left to right we show: i) a
    nontrivial string winding around the system in one of the two possible directions, ii) an open
    magnetic string with two different charged (colored) visons at the end points, iii) a trivial closed
    string. The colors red and blue distinguish the two different sublattices that orient the links.}
    \label{fig:orientedSL}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
  \begin{tabular}{| l | c | c | c | c |}
  	\hline
    type & $n_v$ & $Q_v^{\rm{QDM}}$ & $Q_v^{\rm{FPLM}}$  &  \\
	\hline
    monomer & $0$ & -1 & -2 & $\svrtmon$ \\
	\hline
    dimer & $1$ & 0 & -1 &  $\svrtdmr$ \\
	\hline
    trimer & $2$ & 1 & 0 &  $\svrttrmr$ $\svrttrmrtwo$\\
	\hline
    tetramer & $3$ & 2 & 1 &  $\svrtquat$ \\
	\hline
    pentamer & $4$ & 3 & 2 &  $\svrtpent$ \\
	\hline
  \end{tabular}
  \caption{Defects where $n_v$ dimers touch a vertex and their associated $U(1)$ charges on the A sub-lattice in both the QDM and QFPLM. Defects on the B sub-lattice have opposite charge.}
  \label{tab:defects}
\end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
